---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## Reti 2016 - Quantifying Oldowan Stone Tool Production at Olduvai Gorge, Tanzania

@reti_quantifying_2016 published both an Oldowan archaeological data set and an experimental data set.  This data set can be found on this [figshare page](https://figshare.com/articles/Reti_PLOS_ONE_Data_xlsx/2056551/1) and downloaded as an Excel file.  The data include a variety of variables for whole flakes, including detailed measurements of flake platforms. 


```{r, Reti data set }

library(readxl)
library(ggplot2)
library(dplyr)
library(magrittr)

# Place the Excel file in a subfolder called data before 
# running the following code.

# Read the Excel file and use dplyr to rename some variables
# to remove the spaces.
Reti <- read_xlsx("data/RetiPLOSONEData.xlsx") %>%
  rename(B_Thickness = 'B Thickness',
         P_Cortex = 'P Cortex',
         Platform_Area = 'Platform Area',
         Area_Root = 'Area Root',
         Max_Dimension = 'Max Dimension')    

```

The following figure shows the relationship between platform surface area and flake size (weight).  Both variables are adjusted for their different scales.  Color coding reflects the actual Oldowan data versus the experimental data set.

```{r example}

p = ggplot(Reti, aes(Platform_Area ^(1/2), Weight^(1/3), color = Context))
p = p + geom_point(alpha = .6, size = 1)
p = p + ylab('Weight (Cube Root)')
p = p + xlab('Platform Area (Square Root)')
p = p + theme_minimal()
p

```


