---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## Morales et al. 2015 - Measuring Retouch Intensity in Lithic Tools: A New Proposal Using 3D Scan Data

In this paper, @morales_measuring_2015 propose a method for measuring tool reduction in blades from 3D models.  3D scans of the experimental tools prior to and after reduction are [published here](https://zenodo.org/record/3994208#.X0TKyMgzZJJ).  Additionally there is a Word document with two tables of attribute data on the scanned lithics.

An example of the 3D data is forthcoming, but here is an example of how to read Word docx files directly from a web site, extract the tables automatically, fix the column names, and change European decimal places (with a comma) to decimal places with a period.

```{r download_xls_data}

library(httr)
library(ggplot2)
library(magrittr)
library(dplyr)
library(knitr)
library(docxtractr)

# Check to see if the file exists locally already, 
# and if not, download it from the Zenodo website.
# This extra step is not necessary, but it is a nice
# trick to know for when datasets are often updated
# on a website, and it saves download time when testing
# code.
if (!file.exists('data/Morales_2015_table1.rds')) {
  # Read the Word file directly from the web site
  doc_file =  read_docx("https://zenodo.org/record/3994208/files/Measurements.docx?download=1")
  
  # Extract table 1
  Morales_2015_table1 = docx_extract_tbl(doc_file, tbl_number = 1) 
  
  # Fix the column names
  Morales_2015_table1 = assign_colnames(Morales_2015_table1, 1)

  # More fixing of the column names
  names(Morales_2015_table1)[1:8] = c('ID','Mass_unmod','Vol_unmod','Density',
                                      'Mass_mod','Vol_mod','Mass_deb','Vol_deb')
  
  # Convert commas as decimal indicator to periods
  Morales_2015_table1 = apply(apply(Morales_2015_table1, 2, gsub, patt=",", replace="."), 2, as.numeric)
  
  # Save the result as an R data structure
  saveRDS(Morales_2015_table1, 'Morales_2015_table1.rds') 
  
  # Now do the same for Table 2 in this document
  Morales_2015_table2 = docx_extract_tbl(doc_file, tbl_number = 2) 
  Morales_2015_table2 = assign_colnames(Morales_2015_table2, 1)
  names(Morales_2015_table2)[1:8] = c('ID','Mass_unmod','Vol_unmod','Density',
                                      'Mass_mod','Vol_mod','Mass_deb','Vol_deb')
  Morales_2015_table2 = apply(apply(Morales_2015_table2, 2, gsub, patt=",", replace="."), 2, as.numeric)
  saveRDS(Morales_2015_table2, 'Morales_2015_table2.rds') 
  
} else {
  Morales_2015_table1 = readRDS('data/Morales_2015_table1.rds')
  Morales_2015_table2 = readRDS('data/Morales_2015_table2.rds')
}

```

A view on the attribute data in the first Word table.

```{r}

kable(Morales_2015_table1)

```

And a view on the attribute data in the second Word table.

```{r}

kable(Morales_2015_table2)

```
