---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

## Grove and Blinkhorn 2020 - Neural networks differentiate between Middle and Later Stone Age lithic assemblages in eastern Africa

In their paper, @grove_neural_2020 use neural networks on a dataset of 92 Middle and Later Stone Age assemblages from east Africa.  They publish a dataset of presence/absence data for typological categories for these assemblages, and the code to analyze it and reproduce the results.  

Here we download the raw data and display it.  The complete paper with data and code is open access and can be [found here](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0237528).

```{r load_data}

library(httr)
library(readxl)
library(knitr)

if (!file.exists('data/grove_blinkhorn_2020.rds')) {
  url = "https://doi.org/10.1371/journal.pone.0237528.s002"
  GET(url, write_disk(tf <- tempfile(fileext = ".xlsx")))
  grove_blinkhorn_2020 = read_excel(tf)
  saveRDS(grove_blinkhorn_2020, 'data/grove_blinkhorn_2020.RDS') 
} else {
  grove_blinkhorn_2020 = readRDS('data/grove_blinkhorn_2020.RDS')
}

```

```{r}

kable(grove_blinkhorn_2020)

```
