---
output: github_document
bibliography: bibliography.bib
always_allow_html: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## d'Errico et al. 2011 - PACEA geo-referenced radiocarbon database

Here we use the [c14bazAAR](https://github.com/ropensci/c14bazAAR) R library to download the radiocarbon database compile by @d2011pacea.  We buid a dynamic map showing the site locations from this data set.  See our [Ruebens et al. 2015](https://github.com/davidrbraun/ArchData/tree/master/Ruebens%20et%20al%202015) example for how to make a static map.

```{r, load libraries and the data}

#library(ggplot2)
library(tidyr)
library(dplyr)
library(knitr)
library(leaflet)
library(mapview)
library(utf8)
library(magrittr)
library(utf8)

#webshot::install_phantomjs(force = TRUE)

library(c14bazAAR)
if (!file.exists('data/pacea_ams.rds')) {
  pacea_ams = get_c14data('pacea')
  saveRDS(pacea_ams, 'data/pacea_ams.rds') 
} else {
  pacea_ams = readRDS('data/pacea_ams.rds')
}

```

There are `r nrow(pacea_ams)` cases in this data file.  Here is what the first 10 rows of data look like.

```{r}

kable(pacea_ams[1:10,])

```

Here is a Leaflet version of the map.  When rendered within rStudio this produces a dynamic map that can be zoomed and where each data point shows all of the data attached to that point.

```{r, leaflet version}

htmltitle <- "<h5> PACEA Radiocarbon Database </h5>"

# Fix the UTF8 encoding for the fields to be included
pacea_ams$site = utf8_encode(pacea_ams$site)
pacea_ams$sitetype = utf8_encode(pacea_ams$sitetype)
pacea_ams$period = utf8_encode(pacea_ams$period)
pacea_ams$culture = utf8_encode(pacea_ams$culture)

# For the map, aggregate the data by site (rather than by date)
site_locations = pacea_ams %>%
  select(site, lat, lon) %>%
  distinct()

# And then lump the periods, types (should normally be one already),
# cultures into one text field for each site for the map  
for (i in 1:nrow(site_locations)) {
  site_locations$type[i] = paste(unique(pacea_ams$sitetype[pacea_ams$site == site_locations$site[i]]),
                              collapse = ', ')
  site_locations$period[i] = paste(unique(pacea_ams$period[pacea_ams$site == site_locations$site[i]]),
                                collapse = ', ')
  site_locations$culture[i] = paste(unique(pacea_ams$culture[pacea_ams$site == site_locations$site[i]]),
                                 collapse = ', ')
  site_locations$dates[i] = length(pacea_ams$site[pacea_ams$site == site_locations$site[i]])
}

# Make the labels for each site
mylabels <- paste(
  "Site Name: ", utf8_encode(site_locations$site), "<br/>",
  "Type: ", utf8_encode(site_locations$sitetype), "<br/>",
  "Period: ", utf8_encode(site_locations$period), "<br/>",
  "Culture: ", utf8_encode(site_locations$culture), "<br/>",
  "No. of dates: ", site_locations$dates) %>% lapply(htmltools::HTML)

# Make the interactive map
m <- leaflet() %>%
      addTiles %>%
      addMarkers(data = site_locations,
                  popup = ~site,
                  label = mylabels,
                  labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                              textsize = "13px", direction = "auto")) %>%
      addControl(html=htmltitle, position = "topright")
  
m

```

The following code saves the HTML code from the Leaflet map.  You can view the [dynamic map here](https://davidrbraun.github.io/ArchData/derrico.html).

```{r}

mapshot(m, 'leaflet/index.html')

```

