---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

## Mraz et al. 2020 - Heating reduces the force required to remove a flake

This code fetches a dataset from a controlled experiment to test the effect of heating raw materials on the force required to remove a flake.  The Open Access publication [@mraz_thermal_2019] includes a data set on flakes and on the cores plus some R code to analyze the data and plot the results.  Here we load the flake data and present the data slightly differently by looking at the effect of heating on the force required to remove a flake of a given mass.

```{r load_data}

library(httr)
library(ggplot2)

if (!file.exists('data/mraz_2020.rds')) {
  url = "https://static-content.springer.com/esm/art%3A10.1038%2Fs41598-019-51139-3/MediaObjects/41598_2019_51139_MOESM3_ESM.csv"
  GET(url, write_disk(tf <- tempfile(fileext = ".csv")))
  mraz_2020 = read.csv(tf)
  saveRDS(mraz_2020, 'data/mraz_2020.rds') 
} else {
  mraz_2020 = readRDS('data/mraz_2020.rds')
}

```

Here we build a figure showing that less force is required to remove heat treated flakes of an equivalent weight.  Regression lines are fitted to each data class.  The grey bands represent the confidence intervals on the effect size.

```{r plot_data}
 
p = ggplot(mraz_2020, aes(Wg, Force, color = Temperature))
p = p + geom_point(alpha = .45, size = 1)
p = p + geom_smooth(method = 'lm')
p = p + theme_minimal()
p = p + ylab('Force (Newtons)') + xlab('Weight (gms)')
p

```
