---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```

## Herzlinger and Goren-Inbar 2019 - Beyond a Cutting Edge: a Morpho-technological Analysis of Acheulian Handaxes and Cleavers from Gesher Benot Ya‘aqov, Israel

@herzlinger_beyond_2020 published on the handaxes and cleavers from Gesher Benot Ya‘aqov, Israel, in the *Journal of Paleolithic Archaeology* and placed all of the data on [OSF](https://osf.io/u3n9k/). The data include 3D models of all of the artifacts and a  spreadsheet of attribute values for each including the number of dorsal and ventral scars and the type of blank.  For the 3D models, the data format is something called .3dl which is compatible with the software program AGMT3-D, which was published by in open access by [Gadi Herzlinger and Leore Grosman on PLOS One](https://journals.plos.org/plosone/article?id=10.1371/journal.pone.0207890) and is freely available for download.

We wondered if the data could be used outside of this program by converting the format to something more standard like PLY. In fact, the files are in a standard Matlab format that R can be used to easily convert them. So the code that follows loads each artifact, coverts it to a PLY, saves the file, and then makes a 2D snapshot of each (after rotating them).

```{r load_and_convert_data}

library(rgl)
library(Rvcg)
library(Morpho)
library(R.matlab)
library(ggplot2)
library(png)
library(grid)
library(gridExtra)

# To run this code, first down load the zip file containing the 3D models from this page
# https://osf.io/u3n9k/
# Next, unzip the files to a folder called data.
# This code will then loop through that folder and convert each file to a ply type.

for (filename in list.files('data', pattern = '*.3dl')) {
  new_filename = paste('data/', strsplit(filename,'\\.')[[1]][1], '.ply', sep = '')
  if (!file.exists(new_filename)) {
    
    # Read the MatLab format file
    biface_matlab_format = readMat(paste('data', filename, sep = '//'))
    
    # Convert to a more standardized formet
    biface = tmesh3d(vertices = t(biface_matlab_format$v),
                     indices = t(biface_matlab_format$f),
                     homogeneous = FALSE)
	  
    # Save the result at a PLY
    vcgPlyWrite(biface, new_filename)
  }
}

```

Make a view of each and save as a PNG file.

```{r make_png_of_each}

# use rgl to render each handaxe, rotate it appropriately.  Note this routine does not
# generate proper png files if the documented is knitted.  Instead, just run this code
# block.

open3d()
for (filename in list.files('data', pattern = '*.ply')) {
  new_filename = paste('data/', strsplit(filename,'\\.')[[1]][1], '.png', sep = '')
  if (!file.exists(new_filename)) {
    biface = vcgPlyRead(paste('data', filename, sep = '//'))

    # Do PCA on the vertices to achieve a more standard orientation
	  v = princomp(t(biface$vb[1:3,]), scores = TRUE, cor = FALSE)$scores
	  
	  # Put the PCA scores back in the mesh object along with the texture
    biface$vb[,] = t(cbind(v, biface$vb[4,]))							
	
	  # Rotate into standard view
    biface = rotaxis3d(biface, c(0, 0, 0), c(0, 1, 0), -pi / 2)
    biface = rotaxis3d(biface, c(0, 0, 0), c(0, 0, 1), -pi / 2)

    # Check to see if it looks to be upside down and flip if so
    if (sd(biface$vb[1,biface$vb[3,]<0]) < sd(biface$vb[1,biface$vb[3,]>0])) {
  	  biface = rotaxis3d(biface, c(0,0,0), c(1,0,0), pi) }		

    clear3d()
    
    shade3d(biface, color = '#FFD54F')
    
    snapshot3d(new_filename, fmt = 'png')
  }
}
rgl.close()

```

Now display them.

```{r plot_handaxes, fig.width = 2, fig.height = 2}

par(mfrow=c(10,10))

for (filename in list.files('data', pattern = '*.png')) {
  img <- readPNG(paste('data', filename, sep = '/')) 
  g <- rasterGrob(img, interpolate=TRUE) 
  p = ggplot(data.frame(x = 1:25, y = 1:25), aes(x, y))
  p = p + annotation_custom(g, xmin=-Inf, xmax=Inf, ymin=-Inf, ymax=Inf)
  p = p + xlab('') + ylab('')
  p = p + ggtitle(filename)
  p = p + theme_minimal()
  print(p)
}

```

