---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## Lombao et al. 2020 - A new approach to measure reduction intensity on cores and tools on cobbles: The Volumetric Reconstruction Method

In this paper on quantifying core reduction intensity, @lombao_new_2020 posted a [another large set](https://zenodo.org/record/3368659#.X0TENcgzZJJ) (N = 128) of 3D scans of 64 blanks and 64 cores/handaxes (see also @lombao_effects_2019).  Also included is a spreadsheet of attribute data.

```{r download_xls_data}

library(httr)
library(ggplot2)
library(readxl)
library(magrittr)
library(dplyr)
library(knitr)

# Check to see if the file exists locally already, 
# and if not, download it from the Zenodo website.
# This extra step is not necessary, but it is a nice
# trick to know for when datasets are often updated
# on a website, and it saves download time when testing
# code.
if (!file.exists('data/Lombao_2020.rds')) {
  url = "https://zenodo.org/record/3368659/files/VRM%20experiment%20database.xlsx?download=1"
  GET(url, write_disk(tf <- tempfile(fileext = ".xlsx")))
  Lombao_2020 = read_excel(tf, sheet = 1, skip = 0) 
  saveRDS(Lombao_2020, 'data/Lombao_2020.rds') 
} else {
  Lombao_2020 = readRDS('data/Lombao_2020.rds')
}

# Rename the columns to make them more R friendly
Lombao_2020 = Lombao_2020 %>%
  rename(Original_mass = 'Original mass (mm)') %>%
  rename(Original_surface = 'Original surface (mm2)') %>%
  rename(Original_volume = 'Original volume (mm3)') %>%
  rename(Mass_FTh = 'Mean FTh (Flake thickness) (mm)') %>%
  rename(Scar_generations_1 = 'Scar generations...15') %>%
  rename(Thickness = 'Thickness (mm)') %>%
  rename(Mean_PTh_1 = 'Mean PTh (Platform thickness) (mm)...13') %>%
  rename(Scar_generations_2 = 'Scar generations...12') %>%
  rename(Width = 'Width (mm)') %>%
  rename(Mean_PTh_2 = 'Mean PTh (Platform thickness) (mm)...10') %>%
  rename(Scar_generations_3 = 'Scar generations...9') %>%
  rename(Length = 'Length (mm)') %>%
  rename(Surface = 'Surface (mm2)') %>%
  rename(Final_volume = 'Final volume (mm3)') %>%
  rename(Final_mass = 'Final mass (g)') %>%
  rename(Reduction_strategy = 'Reduction strategy') %>%
  rename(Core_label = 'Core Label') %>%
  rename(Blank_label = 'Blank label')
```

A view on the attribute data.

```{r}

kable(Lombao_2020)

```



