---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## Ruebens, McPherron & Hublin 2015 - On the local Mousterian origin of the Châtelperronian: Integrating typo-technological, chronostratigraphic and contextual data

In @ruebens_local_2015 we included summary data.

```{r, load and clean the data}

library(ggplot2)
library(ggrepel)
library(dplyr)
library(magrittr)
library(knitr)

cp_sites = read.csv("data/CP Sites.csv", header = TRUE, sep = ',')

```

The following figure shows the relationship between median platform depth and median exterior platform angle (EPA) for the studied assemblages.

```{r example}

library(ggmap)
library(ggrepel)
library(raster)
library(mapdata)

europe = raster('data/elevation9x9.tif')

France.map = get_map(location = 'France', zoom = 6, maptype = 'terrain-background')
cp_sites = na.omit(read.delim('data/CP Sites.txt', stringsAsFactors = FALSE, dec = '.', encoding = "UTF-8"))
names(cp_sites)[1] = "Sitename"

ggmap(France.map) + geom_point(data = cp_sites, aes(x=Longitude, y=Latitude),size=1.5, color = 'red') + geom_text_repel(data = cp_sites, aes(x = Longitude, y = Latitude, label = 1:nrow(cp_sites)), nudge_x = 0.05, size = 2.5) + xlab('Longitude') + ylab('Latitude') + ggtitle('Châtelperronian Sites', subtitle = 'Data from Ruebens et al. 2015')
caption = paste(1:nrow(cp_sites), cp_sites$Sitename, collapse = ', ')

```

Assemblage codes - `r caption`

