---
output: github_document
bibliography: bibliography.bib
always_allow_html: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## Ruebens, McPherron & Hublin 2015 - On the local Mousterian origin of the Châtelperronian: Integrating typo-technological, chronostratigraphic and contextual data

In @ruebens_local_2015 we included in the Supplementary Information a spreadsheet of summary data on Châtelperronian sites.  Here we show what some of those data look like by plotting the category 1 and 2 sites and listing some of the data.

```{r, load libraries and the data}

library(ggplot2)
library(ggrepel)
library(dplyr)
library(tidyr)
library(magrittr)
library(readxl)
library(knitr)
library(sf)
library(raster)
library(RStoolbox)
library(leaflet)
library(maptools)
library(ggspatial)
library(ggmap)
library(mapview)
library(tiff)
library(rgdal)

webshot::install_phantomjs(force = TRUE)

# These CSV files are tabs one and two from the spreadsheet in the SI
# of Ruebens et al. 2015.  Some columns, like sitename, have names that need 
# to be corrected.
cp_sites1 = read_excel('data/Ruebens et al 2015.xlsx', sheet = 2, skip = 1) %>%
  rename(Sitename = 'Site name')

cp_sites2 = read_excel('data/Ruebens et al 2015.xlsx', sheet = 3, skip = 1) %>%
  rename(Sitename = 'Site name') %>%
  drop_na()
  
```


```{r, prep the data}

# Need to make an ROI
# Take the sites and create square around it
# Load the sites and make them to sf objects 
cp_sites1_sf <- st_as_sf(cp_sites1, coords = c("Long.", "Lat."), crs = 4326, agr = "constant")
cp_sites2_sf <- st_as_sf(cp_sites2, coords = c("Long.", "Lat."), crs = 4326, agr = "constant")

# Row bind them into one dataframe
cp_sites_sf <- rbind(cp_sites1_sf, cp_sites2_sf)

# And save it as a shapefile
st_write(cp_sites_sf, "data/Reubens_Sites.shp", append = FALSE)

# Read the ROI for Reubens map 
ReubensROI<-st_read("data/Reubens_ROI.shp")

```

Here is a Leaflet version of the map.  When rendered within rStudio this produces a dynamic map that can be zoomed and where each data point shows all of the data attached to that point.

```{r, leaflet version}

htmltitle <- "<h5> Reubens 2015 Archaeological Sites </h5>"

mylabels <- paste(
  "Site Name: ", cp_sites_sf$Sitename, "<br/>",
  "Region: ", cp_sites_sf$Region, "<br/>",
  "Location: ", cp_sites_sf$Concerns) %>% lapply(htmltools::HTML)

m <- leaflet() %>%
      addTiles %>%
      addMarkers(data = cp_sites1_sf,
                  popup = ~Sitename,
                  label = mylabels,
                  labelOptions = labelOptions(style = list("font-weight" = "normal", padding = "3px 8px"), 
                                              textsize = "13px", direction = "auto")) %>%
      addControl(html=htmltitle, position = "topright")
  
m

```

The following code saves the HTML code from the Leafet map.  You can view the [dynamic map here](https://davidrbraun.github.io/ArchData/index.html).

```{r}

mapshot(m, 'docs/index.html')

```

Here is a static map of all Category 1 (Châtelperronian sites with good contextual information) and Category 2 (Châtelperronian sites needing some better contextual information) sites considered in @ruebens_local_2015.

```{r map_version1, dpi = 600}

# Download this base map from https://www.naturalearthdata.com/downloads/
# Here we also used qGIS to clip the map to the area of Europe we are interested in,
# and saved it as a geoTIFF called bgmap.tif
bgmap <- brick("data/bgmap.tif")

map <- ggplot()
map = map + ggRGB(bgmap, r = 1, g = 2, b = 3,  ggLayer = TRUE)
map = map + geom_sf(data = ReubensROI, color = NA, fill = NA)
map = map + geom_sf(data = cp_sites_sf, size = 1.5, color = 'red')
map = map + ggrepel::geom_label_repel(data = cp_sites_sf,
                                      aes(label = Sitename, geometry = geometry),
                                      stat = "sf_coordinates", min.segment.length = 0,
                                      colour = "black", segment.colour = "black",
                                      label.size = 0.2, nudge_x = 0.5, size = 1,
                                      segment.alpha = .5, point.padding = .1,
                                      label.padding = .1)
map = map + ggtitle('Châtelperronian Sites', subtitle = 'Data from Ruebens et al. 2015')
map = map + annotation_scale(location = "bl", width_hint = 0.5) 
map = map + annotation_north_arrow(location = "br", which_north = "true", 
        pad_x = unit(0.25, "in"), pad_y = unit(0.3, "in"),
        style = north_arrow_fancy_orienteering)
map = map + xlab('Longitude') + ylab('Latitude')
map = map + coord_sf()
map 

```

And here is another way of making that same map.  This version better preserves the resolution of the underlying base map.

```{r map_version2, dpi = 600}

# Download this base map from https://www.naturalearthdata.com/downloads/
# Here we also used qGIS to clip the map to the area of Europe we are interested in,
# and saved it as a geoTIFF called bgmap.tif.  You can likely make this map without first clipping it.

# The first line loads the map as a raster dataset.
# The second line reads the spatial limits of the map.
bgmap = as.raster(readTIFF("data/bgmap.tif", native = TRUE, convert = TRUE))
bgmap_limits = readGDAL('data/bgmap.tif')@bbox

map <- ggplot()
map = map + annotation_raster(bgmap,
                          xmin = bgmap_limits[1,1],
                          xmax = bgmap_limits[1,2],
                          ymin = bgmap_limits[2,1],
                          ymax = bgmap_limits[2,2]) 
map = map + geom_sf(data = ReubensROI, color = NA, fill = NA)
map = map + geom_sf(data = cp_sites_sf, size = 1.5, color = 'red')
map = map + ggrepel::geom_label_repel(data = cp_sites_sf,
                                      aes(label = Sitename, geometry = geometry),
                                      stat = "sf_coordinates", min.segment.length = 0,
                                      colour = "black", segment.colour = "black",
                                      label.size = 0.2, nudge_x = 0.5, size = 1,
                                      segment.alpha = .5, point.padding = .1,
                                      label.padding = .1)
map = map + ggtitle('Châtelperronian Sites', subtitle = 'Data from Ruebens et al. 2015')
map = map + annotation_scale(location = "bl", width_hint = 0.5) 
map = map + annotation_north_arrow(location = "br", which_north = "true", 
        pad_x = unit(0.25, "in"), pad_y = unit(0.3, "in"),
        style = north_arrow_fancy_orienteering)
map = map + xlab('Longitude') + ylab('Latitude')
map = map + coord_sf()
map 

```

Here are two views on the data themselves.  First the Category 1 sites.

```{r}

kable(cp_sites1_sf)

```

And the Category 2 sites.

```{r}

kable(cp_sites1_sf)

```

To see this map in google view this file as a kml on google earth

```{r, google earth}

cp_sites_sp<-as(cp_sites_sf, "Spatial")

kmlPoints(cp_sites_sp,kmlfile = "Reubens_map.kml", kmlname="Reubens_map",icon="http://www.gstatic.com/mapspro/images/stock/962-wht-diamond-blank.png", name=paste(cp_sites_sp$Sitename), description = paste(cp_sites_sp$Concerns))


```

