---
output: github_document
bibliography: bibliography.bib
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

```


## Ruebens, McPherron & Hublin 2015 - On the local Mousterian origin of the Ch창telperronian: Integrating typo-technological, chronostratigraphic and contextual data

In @ruebens_local_2015 we included summary data.

```{r, load and clean the data}

library(ggplot2)
library(ggrepel)
library(dplyr)
library(magrittr)
library(knitr)

cp_sites1 = read.csv("data/Reubens_Category_1.csv", header = TRUE, sep = ',')

cp_sites2 = read.csv("data/Reubens_Category_2.csv", header = TRUE, sep = ',')

```

The following figure shows the relationship between median platform depth and median exterior platform angle (EPA) for the studied assemblages.

_SHANNON IS THE TEXT ABOVE LEFT OVER?_

```{r example}

library(ggmap)
library(ggrepel)
library(raster)
library(mapdata)
library(ggplot2)
library(dplyr)
library(sf)
library(raster)
library(sp)
library(tmap)
library(automap)
library(pander)
library(ggrepel)
library(rosm)
library(rasterVis)
library(RStoolbox)
library(ggspatial)
library(RColorBrewer)
library(manipulate) # Included with RStudio
library(lubridate)

```

```{r, various detials}

europe = raster('data/elevation9x9.tif')

#France.map = get_map(location = 'France', zoom = 6, maptype = 'terrain-background')

#cp_sites = na.omit(read.delim('data/CP Sites.txt', stringsAsFactors = FALSE, dec = '.', encoding = "UTF-8"))

#need to make an ROI
#Take the sites and creata square around it
#Load the sites and make them to sf objects 
cp_sites1_sf<-st_as_sf(cp_sites1, coords = c("Long.", "Lat."), crs = 4326, agr = "constant")

cp_sites2_sf<-st_as_sf(cp_sites2, coords = c("Long.", "Lat."), crs = 4326, agr = "constant")


names(cp_sites1_sf)[1] = "Sitename"
names(cp_sites2_sf)[1] = "Sitename"

cp_sites1_sf$Concerns=NA
cp_sites_sf<-rbind(cp_sites1_sf,cp_sites2_sf)

#Now out put them as shapefiles

st_write(cp_sites_sf,"Reubens_Sites.shp")

#Read in ROI for Reubens map 

ReubensROI<-st_read("data/Reubens_ROI.shp")


```


Load in maps and the distriubtuion of sites



```{r, maps}




bgmap<-brick("data/bgmap.tif")


reubensmap2<-ggplot()+
ggRGB(bgmap, r=1, g=2, b=3,  ggLayer = TRUE)+
  geom_sf(data=ReubensROI,color=NA,fill=NA)+
geom_sf(data=cp_sites_sf,size=1.5, color = 'red')+
  ggrepel::geom_label_repel(data=cp_sites_sf, aes(label=Sitename, geometry=geometry), stat= "sf_coordinates", min.segment.length = 0, colour= "black",segment.colour="black",label.size = 0.4,nudge_x = 0.5, size = 1.7, segment.alpha = .5,point.padding = .3)+
   ggtitle('Ch창telperronian Sites', subtitle = 'Data from Ruebens et al. 2015')+
   xlab('Longitude') + ylab('Latitude')+
  coord_sf()
  
reubensmap2


reubensmap1<-ggplot()+
  ggR(europe, stretch="hist", ggLayer = TRUE, geom_raster=TRUE)+
  scale_fill_gradientn(name="Altitude",colours = terrain.colors(300))


reubensmap2<-ggplot()+
  geom_sf(data=cp_sites_sf)+
  ggrepel::geom_label_repel(data=cp_sites_sf, aes(label=Sitename, geometry=geometry), stat= "sf_coordinates", min.segment.length = 0, colour= "black",segment.colour="black",nudge_x = 0.05, size = 2.5)+
#  coord_sf()+
  ggtitle('Ch창telperronian Sites', subtitle = 'Data from Ruebens et al. 2015')



#ggmap(France.map) + geom_point(data = cp_sites, aes(x=Longitude, y=Latitude),size=1.5, color = 'red') + geom_text_repel(data = cp_sites, aes(x = Longitude, y = Latitude, label = 1:nrow(cp_sites)), nudge_x = 0.05, size = 2.5) + xlab('Longitude') + ylab('Latitude') + ggtitle('Ch창telperronian Sites', subtitle = 'Data from Ruebens et al. 2015')
#caption = paste(1:nrow(cp_sites), cp_sites$Sitename, collapse = ', ')

```

Assemblage codes - `r caption`

